---
title: "Reproducible Research: Peer Assessment 1"
output: html_document
keep_md: true
---


## Loading and preprocessing the data

```{r}
library(tidyverse)
library(knitr)
activity_df = read_csv(file = "activity.csv")

```


## What is mean total number of steps taken per day?
For this part of the assignment, you can ignore the missing values in the dataset.

### Calculate the total number of steps taken per day.

```{r}
atb = activity_df %>%
    group_by(date) %>%
    summarise(total_steps = sum(steps)) 
kable(atb, format = "html")
```

###  Make a histogram of the total number of steps taken each day
```{r}
activity_df %>%
    group_by(date) %>%
    summarise(total_steps = sum(steps)) %>%
    ggplot() +
    geom_histogram(mapping = aes(x=total_steps))
```

###  Calculate and report the mean and median of the total number of steps taken per day

```{r}
activity_df %>%
    drop_na() %>%
    summarise(mean = mean(steps), median = median(steps))
```


## What is the average daily activity pattern?



## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
